Crystals

### 2017-02-19 doc/ms.tex
Bayes paragraph

\section{The prior information}

>>>>

\section{The prior information}
In the Bayesian framework, probability distributions are used to model
states of uncertainty about the values of unknown quantities.
Typically, one starts with the ``prior distribution''
for unknown quantities (`parameters') $\params$, written $p(\params | \info)$
(the probability distribution for $\params$ {\em given} prior information
$\info$). This is supplemented with $p(\data | \params, \info)$,
which describes the uncertainty about the data which we {\em would} have,
if we knew the parameters (and the prior information). The
product of these is the joint prior
\begin{align}
p(\params, \data | \info) &= p(\params | \info)p(\data | \params, \info).
\end{align}
Once a specific observed dataset $\data_o$ is known, knowledge about
$\params$ is updated from the prior to the posterior
\begin{align}
p(\params | \data, \info) &\propto
    p(\params | \info)p(\data_o | \params, \info).
\end{align}
which takes the data into account.
